\begin{thebibliography}{x}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{steinemannFire}
  Denis Steinemann,
  \textit{Simulation and Animation of Fire}, \\
  A presentation in Seminar on Physically-based Methods for 3D-Games and Medical Applications, 2002.

\bibitem{wikiGameEngine}
  Wikipedia,
  \textit{Game engine}, \\
  \url{https://en.wikipedia.org/wiki/Game_engine}, Internet, 2018.

\bibitem{wikiQuake}
 Wikipedia, 
 \textit{Quake engine},\\
 \url{https://en.wikipedia.org/wiki/Quake_engine}, Internet, 2018.
  
\bibitem{MDLformat}
 David Henry, 
 \textit{MDL file format (Quake's models)},\\
 \url{http://tfc.duke.free.fr/coding/mdl-specs-en.html}, 2004. december 20.
 
\bibitem{wikiQuake2}
 Wikipedia, 
 \textit{Quake II engine},\\
 \url{https://en.wikipedia.org/wiki/Quake_II_engine}, Internet, 2018.

\bibitem{fsQuake2}
 Fabien Sanglard, 
 \textit{Quake 2 Source Code Review},\\
 \url{http://fabiensanglard.net/quake2/quake2_opengl_renderer.php}, 2011. szeptember 16.
 
\bibitem{MD2format}
 David Henry, 
 \textit{MD2 file format (Quake 2's models)},\\
 \url{http://tfc.duke.free.fr/coding/md2-specs-en.html}, 2004. december. 19.

\bibitem{wikiQuake3}
 Wikipedia, 
 \textit{id Tech 3},\\
 \url{https://en.wikipedia.org/wiki/Id_Tech_3}, Internet, 2018.
 
\bibitem{fsQuake3}
  Fabien Sanglard, 
  \textit{Quake 3 Source Code Review},\\
  \url{http://fabiensanglard.net/quake3/renderer.php}, 2012. június 30.

\bibitem{quake3shaderManual}
  Paul Jaquays, Brian Hook
  \textit{Quake III Arena Shader Manual},
  December 23, 1999

\bibitem{wikUE4}
 Wikipedia, 
 \textit{Unreal Engine},\\
 \url{https://en.wikipedia.org/wiki/Unreal_Engine#Unreal_Engine_4}, Internet, 2018.

\bibitem{UEngineFireExample}
 Unreal Engine Documentation, 
 \textit{Fire Examples},\\
 \url{https://docs.unrealengine.com/en-us/Resources/Showcases/Effects/FireExamples}, Internet, 2018.
 
\bibitem{firePhysics2}
 Anne Marie Helmenstine, Ph.D., 
 \textit{What Is Fire Made Of?},\\
 \url{https://www.thoughtco.com/what-is-fire-made-of-607313}, 2017. szeptember 8.

\bibitem{firePhysics1}
 Anne Marie Helmenstine, Ph.D., 
 \textit{Is Fire a Gas, Liquid, or Solid?},\\
 \url{https://www.thoughtco.com/what-state-of-matter-is-fire-604300}, 2017. szeptember 4.

\bibitem{swhThreeDimensionalReconst}
  Samuel William Hasino,
  \textit{Three-Dimensional Reconstruction of Fire from Images},
 2002.

\bibitem{texturedForces}
  Jake Lever, Taku Komura,
  \textit{Real-time controllable fire using textured forces},
2012.

\bibitem{firestarter}
  Marc de Kruijf,
  \textit{firestarter – A Real-Time Fire Simulator}, Internet, 2018.

\bibitem{ArNiStructuralModeling}
Lamorlette, Arnauld, and Nick Foster: \emph{Structural modeling of flames for a production environment}. ACM Transactions on Graphics (TOG). Vol. 21. No. 3. ACM, 2002.
 
\bibitem{wikiOGL}
 Wikipedia, 
 \textit{OpenGL},\\
 \url{https://en.wikipedia.org/wiki/OpenGL}, Internet, 2018.
 
 \bibitem{freeGlut}
 Freeglut, 
 \textit{Hivatalos weboldal},\\
 \url{http://freeglut.sourceforge.net}, Internet, 2018.
 
  \bibitem{glew}
 The OpenGL Extension Wrangler Library, 
 \textit{Hivatalos weboldal},\\
 \url{http://glew.sourceforge.net}, Internet, 2018.
 
  \bibitem{glm}
 OpenGL Mathematics, 
 \textit{Hivatalos weboldal},\\
 \url{https://glm.g-truc.net/0.9.8/index.html}, Internet, 2018.

  \bibitem{soil}
Simple OpenGL Image Library, 
 \textit{Hivatalos weboldal},\\
 \url{https://www.lonesock.net/soil.html}, Internet, 2018.

\end{thebibliography}

